Providing a Unified Software Environment for Canada’s National Advanced Computing Centers

### 2019-03-21 paper.tex
Added details about EasyBuild

EasyBuild originated from the University of Ghent, but now has over 200 contributors from around the world. The framework is based on scripted recipes to install packages, usually from source code. It is designed to create optimized binaries, and eases recompilation of multiple versions of a given application using many combinations of compilers or libraries.

>>>>

EasyBuild originated from the University of Ghent, but now has over 200 contributors from around the world. The framework is based on scripted recipes (in Python) to install packages, usually from source code. It is designed to create optimized binaries, and eases recompilation of multiple versions of a given application using many combinations of compilers or libraries. EasyBuild is composed of three parts: the framework, the EasyBlocks, and the EasyConfigs.

The framework contains all of the core code which drives the logic of installing a software. It drives all of the steps necessary to install a software: parsing the configuration options, downloading source files, patching them, configuring, building and installing the software, as well as performing post-installation steps such as sanity checks, generating a module or running custom commands.

Written in Python, EasyBlocks define what needs to be done at each step for a given software package. There are generick EasyBlocks, such as {\it ConfigureMake} or {\it CMakeMake}, as well as custom EasyBlocks for packages that have more complicated installation procedures, such as OpenFOAM or PETSc.

EasyConfigs files parametrize the execution of the code from the EasyBlocks. They define the software name and version, the URL from which the source files can be downloaded as well as options to be used for the various steps.

In most cases, there is already an EasyBlock for a given software package, or it can be installed easily with one of the generic EasyBlocks. In these cases, writing a new recipe is as simple as editing a configuration file. EasyBuild also supports command line options to reuse and existing EasyConfig file, while changing the software version or the toolchain being used.

Toolchains are a core concept in EasyBuild. They represent a set or subset of a compiler, and MPI implementation, mathematical libraries and CUDA. Having the ability to generate multiple builds of a given software simply by providing a command line argument to change the toolchain has proven unvaluable to our workflow, and has allowed us to recompile hundreds of packages in matter of days when deploying a new version of compiler or a cluster with a new CPU architecture.
